MSTK: Mesh Toolkit, v 1.7

### 2010-03-23 docs/MSTK.tex
Added LAUR numbers and acknowledgement

\title{MSTK: Mesh Toolkit, v 1.7 - DRAFT}

\author{Rao V. Garimella \\
  T-5, Theoretical Division, \\
  Los Alamos National Laboratory, Los Alamos, NM, USA. \\ E-mail:
  rao@lanl.gov}

@@

>>>>

\title{MSTK: Mesh Toolkit, v 1.7}

\author{Rao V. Garimella \\
  T-5, Theoretical Division, \\
  Los Alamos National Laboratory, Los Alamos, NM, USA. \\ E-mail:
  rao@lanl.gov \\
  \vspace{5em}
  LA-UR-04-0878}

@@

\section{Acknowledgements}

This work was performed under the auspices of the National Nuclear
Security Administration of the US Department of Energy at Los Alamos
National Laboratory under contract No. DE-AC52-06NA25396 with partial support
from the Advanced Simulation Capability (ASC) program.

This manual has been reviewed by LANL and deemed suitable for unlimited
release (LA-UR-04-0878). MSTK has been reviewed by LANL and deemed suitable
for unlimited distribution (LA-CC-04-010). MSTK is distributed under
an LGPL open-source license.
